Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-24 ms.qmd
Update to table

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-labels: "Table"
---

@@

  } else{
        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
}

@@

Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-figs1).

@@

```{r}
#| label: tbl-tabs1
#| tbl-cap: Model estimates, standard error, and 95% credible intervals

@@

# Headers for the table to indicate fixed and random effects
  fixed_head <- c("Fixed Effects", rep(" ", 4))
  random_head <- c("Random Effects", rep(" ", 4))

>>>>

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: true
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-labels: "Table"
---

@@

  } else{
        model3.2 <- readRDS("./output/models/lnVRQ10_3.2")
  model3.2_bayes <- readRDS("./output/models/lnVRQ10_3.2_bayes")
}
str(summary(model3.2_bayes)
)
######################################################
  # Bayesian Contrasts
######################################################

@@

Analysis of $lnVR_{Q_{10}}$ suggested that variance increases with higher temperatures across all habitat types, with terrestrial ectotherms having the smallest increase in variance (@fig-figs1). @tbl-tabs1

@@

```{r}
#| label: tbl-tabs1
#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types. Models estimates are based off `r summary(model3.2_bayes)$nobs` effect sizes from `r summary(model3.2_bayes)$ngrps$record_num` studies.

@@
